---
name: "Jhon Flores Rojas"
position: ""
phone: "+51 947178779"
email: fr.jhonk@gmail.com 
github: Tjhon 
linkedin: jhon-kevin-flores-rojas-a19133196
aboutme: "Proactivo"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::moderncv:
    theme: classic
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  warning = FALSE, 
  message = FALSE, 
  fig.align = 'center', 
  results = "asis", 
  out.height = "90%", 
  out.width = "90%"
)
library(vitae)
library(tidyverse)
library(lubridate)
library(here)
library(readxl)
library(glue)
library(conflicted)

library(googlesheets4)
gs4_deauth()

conflict_prefer("filter", "dplyr") # para evitar conflictos
conflict_prefer("here", "here")
```

# Datos personales
```{r datos}
datos <- read_sheet("https://docs.google.com/spreadsheets/d/1PuEDxmZeVdw18Mv2SR5BssCFSfaB2xF60Hxle_nbcUU/edit?usp=sharing")

#edu <- read_sheet("https://docs.google.com/spreadsheets/d/1JaAIVolNV9kAeHidlh8zpsbiTVF5nEeF0OkLRryI7Rc/edit?usp=sharing")

educ <- read_sheet("https://docs.google.com/spreadsheets/d/1JaAIVolNV9kAeHidlh8zpsbiTVF5nEeF0OkLRryI7Rc/edit?usp=sharing")

cursos <- read_sheet("https://docs.google.com/spreadsheets/d/1GNg61ATPZz9q1UQUxf4ibmdD_qBFe_WjK0peuW6CH2E/edit?usp=sharing")

programas <- read_sheet("https://docs.google.com/spreadsheets/d/1NMSuEEPt7DOWIlNf5RaMCiAFWQ4vV-NjkjjsoX6nLJA/edit?usp=sharing")

#mooc <- read_sheet("https://docs.google.com/spreadsheets/d/16x9Uv-ULH_bEXDJs9A3df_xCmAwlBUoB7DYdr7ETOOU/edit?usp=sharing")

hab <- read_sheet("https://docs.google.com/spreadsheets/d/15zLj8Bgk9BEUBISCY_zWFPtxPNKztihufOXzG-MMm70/edit?usp=sharing")

```


```{r}
datos %>% 
  mutate(entrada = as.character((entrada))) %>% 
  #fill(names(datos)) %>% 
  brief_entries(when = datos, 
                with = entrada) 
```




# Educación 

```{r}
educ %>% arrange(desc(final)) %>% 
  detailed_entries( 
    when = glue("{inicio}-{final}"),
    what = que,
    where = region,
    with = lugar,
    .protect = FALSE)

```

# Cursos y proyectos 

```{r}
cursos %>% arrange(desc(final)) %>% 
  detailed_entries(
    when = final,
    what = como, 
    where = lugar,
    with = institucion,
    why = que
  )
```


# Programas informaticos

```{r}
programas %>% 
  fill(names(programas)) %>%
  detailed_entries(
    when = habilidad,
    what = programa, 
    why = que)
```


# Habilidades

```{r}
hab %>% detailed_entries(
  what = area,
  why = programas
)
```


# Cursos en linea

## DataCamp

- Introduction to Git
- Introduction to tidyverse
- Writting Eficient R Code
- Introduction to Data Visualization with GGplot
- Intermediate R
- Foundations of Functional Programing With Purrr
- Forecasting in R
- Data Visualization with GGplot2 (Part 1)
- Data Visualization With GGplot2 (Part 2)

## 365 DataScience

- Introduction to python
- Introduction to R programming
- Matemathics
- Introduction to Data Science

## JuliaAcademy

- Introduction to Julia
- Julia for Data Science 
\newpage

